\section{Research Agenda}

The research agenda of this project is ‘what are the most dominant topics in H.P. Lovecraft’s 
writings over his lifespan?’. The goal is to understand how they relate to Lovecraft’s personal 
life experiences, historical events, cultural and social influences, as well as to the broader 
literary and intellectual traditions of his time. To answer that question we will apply topic 
modeling to each of his works in chronological order. By comparing the resulting main topics 
we hope to find changes in the lore of his mythos as well as correlations to the main events 
in his life.\\

We will use computational methods like text processing and tokenization to 
represent the main themes of Lovecraft’s writings from a corpus of all of his works. Because 
Lovecraft died over 70 years ago, many of his writings are public domain and can easily be 
accessed from various institutions providing good coverage for the material. Nevertheless, 
some of the works he contributed are still not public domain, since some authors he worked 
with lived on longer than he did (e.g. Clark Ashton Smith died 1961). This is part of the 
reason why we decided to only cover works solely written by Lovecraft himself. The more 
important reason is that mixing up his writings with ghostwritten or co-written works could 
alter the results since we only want to cover Lovecraft’s themes. Using the programming 
languages Python and R, we first format the corpus into a collection of all works (using 
Python), then process the texts to remove annotations and unnecessary titles and use topic 
modeling on the corpus to gather and represent the data (using R). After that, we will analyze 
the gathered data represented as a plotted diagram in R. That way we can create a timeline-like 
graphic of the main themes and motifs in Lovecraft’s works and discuss them in retrospect to 
events or that time or his personal life.\\

Lovecraft works can be distincted into phases. We will stretch the phase ‘Early Work’ 
up to his first writings, when he was a child. That gives us the following phases:
\begin{itemize}
    \item Phase 1: Early Work (1905-1920)
    \item Phase 2: First Mythos (1920-1923)
    \item Phase 3: Middle Years (1926-1928)
    \item Phase 4: Later Mythos (1930-1934)
\end{itemize}
We will take these phases of his life into account when comparing his lifetime events 
with the results from the topic modeling later.\\

To properly find correlations between his writings and private life or social events of his 
time, we will shortly examine his letters as well as his biographical records. After that, 
we include the ideas and insight into the discussion. We expect to find results in this aspect, 
since Lovecraft is known for his rejection of modern movements of that time. He was known for 
his dislike of New York City, after living there for a period of his life. This is one of the 
interesting parts of his life we hope to find reflected in his writings. We already know of 
the story ‘The Horror at Red Hook’ (1925) in which Lovecraft negatively reflects on Red Hook, 
Brooklyn. It is also important to mention that Lovecraft condemned ethnical groups he encountered 
during his time in New York, mainly Afro-Americans and Asian immigrants. It is no secret that 
Lovecraft used racist slurs and sometimes even antisemitic stereotypes in his writings, all 
of which will be analyzed according to his personal events to explore how his prejudices shaped 
his writing. For all of these aspects of his life, 
we hope to find a similar pattern in his writing through which one could pair a batch of his 
works to a phase of his life.