\section{Data Overview}

The data for this project can be found on Kaggle. We decided to go with this dataset because it 
features all of Lovecraft's written texts in .txt. format, which makes it easy to process the data. 
All stories exist in the public domain and are not subject to copyright. Due to the stories being 
public domain, and more datasets being available online as well as raw HTML texts available, we 
had many sources to choose from. A comparison with other sources and physical prints of stories 
does not indicate any biases or alterations in the texts. Though we have found some works in the 
dataset that are not solely written by Lovecraft since he collaborated with many other authors of 
his time and even took ghostwriting commissions. Another problem also occurred with other datasets, 
where the earliest works of Lovecraft are missing. We decided to still go with this dataset and 
remove works that we don't want to include. Since our research question wants to only cover 
Lovecraft's ideas and writings, the influence of other authors or commissioners could alter the 
results. That's because the ideas of Lovecraft are not really present in these specific writings, 
though his stylometry may be the same.\\

The dataset contains 102 works of Lovecraft, including all collaborations. As we just mentioned, 
collaborations, revisions, and ghost writings are not the subject of this project and will be 
removed. An overview of all the works written solely by Lovecraft, his fiction, can be found in 
his bibliography on Wikipedia. In this case, only his 'fiction' will be included in this project 
as well as some of his works found under 'Juvenilia', which include his earliest writings when he 
was young. Also not included in this project are his poetry works, philosophical works, and 
scientific works since they are either too short or provide no information regarding his mythos 
and lore. After only keeping the works of Lovecraft from the bibliography, the dataset has 70 
stories remaining. These works can be distinguished into short stories, novellas, or even fragments 
from letters or novellas. Lovecraft's works largely vary in length, some just a few pages, and 
other whole novellas. Fragments could also contain just a few paragraphs. One example is the 
story 'Azatoth' (written June 1922), which is very short in length and was supposed to be part 
of a whole novella, though only this fragment survived. It is currently unknown how many such 
fragments were lost, but his wife admitted to having burned a lot of his letters. If these included 
other fragments or whole works of Lovecraft not yet published or copied at that time, that means 
that some works are lost forever.\\

The 70 works in this modified dataset are .txt documents. The text files contain the title and 
the raw text. We formatted the files using R and pasted them into a .csv format. In this process, 
we also added the dates as a second row to the text and manually put another line between 
paragraphs to process them using regular expressions. The file to process the dataset can be 
found in the repository as \texttt{format.r}. The .csv file contains for every text the text\_id, then 
for every paragraph of the text the doc\_id, the title, the date, and the paragraph containing 
the text. This way we can later use topic modeling on the csv to create a timeline-like plot of 
the main themes. The dates found in different sources can be misleading since some stories were 
published after Lovecraft's death. One example is the story 'The Case of Charles Dexter Ward', 
which was written in 1927, partly published in 1941, and fully published in 1943, while Lovecraft 
already died in 1937. The dates we manually added to each file represent the date a work was 
written as provided on WikiSource. This corresponds better to his personal life and events. For 
dates where only the year is provided (see 'The Alchemist', 1908) or no explicit month 
(see 'The Street', late 1919) we used proper months according to quarters or the beginning of 
seasons. For plain years we added the January of that year. Taking into account publishing dates 
is no option since they do not reflect Lovecraft's personal events, may not be in order, or even 
have been published after his death as already mentioned.