\newpage

\begin{thebibliography}{9}
\itemsep0em

\bibitem{wohleber}
Wohleber, C. (1995). \emph{The Man Who Can Scare Stephen King}. Retrieved Feb 17 2023, from \href{https://www.americanheritage.com/man-who-can-scare-stephen-king}{https://www.americanheritage.com/man-who-can-scare-stephen-king}

\bibitem{kirschenbaum}
Kirschenbaum, M. (2010). \emph{What Is Digital Humanities and What's It Doing in English Departments?}. Retrieved Feb 17 2023, from \href{https://dhdebates.gc.cuny.edu/read/untitled-88c11800-9446-469b-a3be-3fdb36bfbd1e/section/f5640d43-b8eb-4d49-bc4b-eb31a16f3d06}{https://dhdebates.gc.cuny.edu/read/untitled-88c11800-9446-469b-a3be-3fdb36bfbd1e/section/f5640d43-b8eb-4d49-bc4b-eb31a16f3d06}

\bibitem{nyhan}
Nyhan, J., \& Plotnikova, M. (Eds.). (2019). \emph{One origin of Digital Humanities}. Springer International Publishing.

\bibitem{romano}
Romano, A. (2020). \emph{Lovecraftian horror — and the racism at its core — explained}. Retrieved Feb 21 2023, from \href{https://www.vox.com/culture/21363945/hp-lovecraft-racism-examples-explained-what-is-lovecraftian-weird-fiction}{https://www.vox.com/culture/21363945/hp-lovecraft-racism-examples-explained-what-is-lovecraftian-weird-fiction}

\bibitem{lc}
H. P. Lovecraft bibliography (2023). In \emph{Wikipedia}. Retrieved Feb 21 2023, from \href{https://en.wikipedia.org/w/index.php?title=H._P._Lovecraft_bibliography&oldid=1135325435}{https://en.wikipedia.org/w/index.php?title=H.\_P.\_Lovecraft\_bibliography\&oldid=1135325435}

\bibitem{joshi}
Joshi, S. T., \& Schultz, D. E. (2001). \emph{An H. P. lovecraft encyclopedia}. Greenwood Press. 

\bibitem{wiki}
Author:Howard Phillips Lovecraft (2023). In \emph{Wikisource} . Retrieved Mar 7 2023, from \href{https://en.wikisource.org/w/index.php?title=Author:Howard_Phillips_Lovecraft&oldid=12959276}{https://en.wikisource.org/w/index.php?title=Author:Howard\_Phillips\_Lovecraft\&oldid=12959276}

\bibitem{blei}
Blei, D. (2012). \emph{Topic Modeling and Digital Humanities}. Retrieved Mar 01 2023, from \href{https://journalofdigitalhumanities.org/2-1/topic-modeling-and-digital-humanities-by-david-m-blei/}{https://journalofdigitalhumanities.org/2-1/topic-modeling-and-digital-humanities-by-david-m-blei/}

\bibitem{gusta}
Gustafson, K. (2005). \emph{Beyond the mountain of madness : a look at the shared themes of Edgar Allan Poe and H.P. Lovecraft (Dissertation)}. Retrieved from \href{http://urn.kb.se/resolve?urn=urn:nbn:se:ltu:diva-43672}{http://urn.kb.se/resolve?urn=urn:nbn:se:ltu:diva-43672}

\bibitem{wiki2}
Supernatural Horror in Literature (2023). In \emph{Wikisource}. Retrieved Mar 07 2023, from \href{https://en.wikisource.org/w/index.php?title=Supernatural_Horror_in_Literature&oldid=12891211}{https://en.wikisource.org/w/index.php?title=Supernatural\_Horror\_in\_Literature\&oldid=12891211}

\bibitem{church}
Church, M. A. (2013). \emph{The Lovecraft Look: An Examination of Lovecraftian Themes in Film}. Find at \href{https://digitalcommons.buffalostate.edu/english\_theses/11}{https://digitalcommons.buffalostate.edu/english\_theses/11}

\bibitem{smith}
Smith, P. (2011). \emph{Re-visioning Romantic-Era Gothicism: An Introduction to Key Works and Themes in the Study of H.P. Lovecraft}. Retrieved Mar 01 2023, from \href{https://doi.org/10.1111/j.1741-4113.2011.00838.x}{https://doi.org/10.1111/j.1741-4113.2011.00838.x}

\bibitem{holmes}
Holmes, F. (2022). \emph{Determining the Number of Topics to Retain using Tools from Factor Analysis}. Vol. 11, No. 1, 1-14. Find at \href{https://doi.org/10.47260/jsem/1111}{https://doi.org/10.47260/jsem/1111}

\bibitem{schultz}
Schultz, D. E., \& Joshi, S. T. (Eds.) (2011). \emph{An epicure in the Terrible: A centennial anthology of essays in honor of H.P. Lovecraft}. New York, NY. Hippocampus Press. 

\bibitem{joshi2}
Joshi, S. T. (1996). \emph{A Subtler Magick: The Writings and Philosophy of H.P. Lovecraft (Third ed.)}. Berkeley Heights, NJ. Wildside Press. page 79

\bibitem{carter}
Carter, L. (1996). \emph{Lovecraft: A look behind the "Cthulhu mythos"}. San Bernardino, CA. Borgo Press. 

\bibitem{letter}
Lovecraft, H.P. (1968). \emph{H. P. Lovecraft, Selected Letters vol. 2}. United States. Arkham House, p. 27

\end{thebibliography}